|

### 2023-02-02 paper.Rmd
Thu Feb  2 08:00:07 CET 2023: update-remote.sh

REG_MED_BESTSIZE <- py$D_AIRFOIL_2hl$REG_MED_BESTSIZE
PT_MED_BESTSIZE <- py$D_AIRFOIL_2hl$PT_MED_BESTSIZE
GP_MED_BESTSIZE <- py$D_AIRFOIL_2hl$GP_MED_BESTSIZE

@@

Since previous work by @dae-gp_2022_symreg demonstrated that DAE-GP, for a given number of 10.000 fitness evaluations, is able to produce solutions that are much smaller in tree size that regular GP, I also studied the influence of pre-training on the size of solutions found by DAE-GP. Figure \@ref(fig:airfoil-size-combined-30gens) shows the median of both the average size of individuals inside the population as well as the size of the currently best performing solution inside the population. It can be observed that both DAE-GP variants strongly reduce the average solutions size already in the first generations and that the average solution size inside the population constantly stays at this very low level for the rest of the search. Regarding the size of the best solution per generation, the results show that the pre-trained version of algorithm did produce solutions with the same median size as traditional DAE-GP. The median size

>>>>

REG_MED_BESTSIZE <- py$D_AIRFOIL_2hl$REG_MED_BESTSIZE
PT_MED_BESTSIZE <- py$D_AIRFOIL_2hl$PT_MED_BESTSIZE
GP_MED_BESTSIZE <- py$D_AIRFOIL_2hl$GP_MED_BESTSIZE
REG_MED_AVGSIZE <- py$D_AIRFOIL_2hl$REG_MED_AVG_SIZE
PT_MED_AVGSIZE <- py$D_AIRFOIL_2hl$PT_MED_AVG_SIZE

@@

Since previous work by @dae-gp_2022_symreg demonstrated that DAE-GP, for a given number of 10.000 fitness evaluations, is able to produce solutions that are much smaller in tree size that regular GP, I also studied the influence of pre-training on the size of solutions found by DAE-GP. Figure \@ref(fig:airfoil-size-combined-30gens) shows the median of both the average size of individuals inside the population as well as the size of the currently best performing solution inside the population. It can be observed that both DAE-GP variants strongly reduce the average solutions size already in the first generations and that the average solution size inside the population constantly stays at this very low level for the rest of the search. The median average size over all generations is `r round(REG_MED_AVGSIZE, 3)` for DAE-GP and `r round(PT_MED_AVGSIZE, 3)` for pre-trained DAE-GP. Regarding the size of the best solution per generation, the results show that the pre-trained version of algorithm did produce solutions with the same median size as traditional DAE-GP. The median size of the best solutions found after terminating the search is the same for both algorithms (DAE-GP: `r round(REG_MED_BESTSIZE, 3)`, Pre-Trained DAE-GP: `r round(PT_MED_BESTSIZE, 3)`)
